\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=0.8in}
\usepackage{enumitem}
\usepackage{hyperref}
\begin{document}
\thispagestyle{empty}
\begin{center}
\noindent \Large{\textbf{Evan DePosit}}\\
\large{Portland, OR}\\
\large{ejdeposit@gmail.com $\bullet$ (503) 799 - 6585}\\
\href{http://evandeposit.com}{\large{evandeposit.com}} $\bullet$
\href{http://github.com/ejdeposit}{\large{github.com/ejdeposit}}\\
\href{http://www.linkedin.com/in/evan-deposit}{\large{linkedin.com/in/evan-deposit}}
\end{center}
\medskip
% ----------------------------------
%         Skills
% ----------------------------------
\textbf{LANGUAGES:} Python, JavaScript, Java, CSS, HTML, SQL, C, Bash, Haskell\medskip \\
\textbf{SKILLS:} Git, Google Cloud Platform, Node.js, Express.js, jQuery,  MongoDB, Bootstrap, Pandas
%Parse, Maven
\bigskip\\
% -------------------------
%         education 
% -------------------------
\noindent
\makebox[0pt][l]{\rule[-.2\baselineskip]{\linewidth}{.3mm}}% 
\large{\textbf{EDUCATION}} \smallskip \\
%
\textbf{Master of Science in Computer Science}, GPA: 3.98
\hfill \textbf{2020}\\ 
Portland State University, Portland, OR
\medskip \\
%
\textbf{Master of Arts in Teaching}, GPA: 4.0
\hfill \textbf{2012}\\
Lewis \& Clark College, Portland, OR
\medskip \\
%
\textbf{Bachelor of Science in Biology}, GPA: 3.75
\hfill \textbf{2008}\\
University of Oregon, Eugene, OR
\bigskip\\
% -----------------------------
%         work experience
%------------------------------
\makebox[0pt][l]{\rule[-.2\baselineskip]{\linewidth}{.3mm}}% 
\large{\textbf{WORK EXPERIENCE}}\smallskip \\
%
\textbf{Full Stack Developer Intern} \hfill \textbf{June 2020 - Sep. 2020}\\
\textsl{PixaMed, Beaverton, OR} 
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=5pt]
	\item Developed features allowing patients to share personal information with their medical providers in a telemedicine web application using Node.js and MongoDB.
	\item Designed and implemented a service, utilizing Google Cloud API's, to allow users to find nearby pharmacies.
	\item Improved the existing code-base by introducing Bootstrap grid to achieve responsive design.
	\item Translated high-level requirements and customer needs into reliable and intuitive functionality.
\end{itemize}
\medbreak \noindent
%
\textbf{Science Teacher} \hfill \textbf{Aug. 2012 - June 2018}\\
\textsl{Liberty High School, Hillsboro, OR, Aug. 2014 - June 2018}\\
\textsl{Westview High School, Beaverton, OR, Jan. 2014 - June 2014}\\
\textsl{JW Poynter Middle School, Hillsboro, OR, Sep. 2013 - Dec. 2013}\\
\textsl{Liberty High School, Hillsboro, OR, Aug. 2012 - June 2013}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=5pt]
	\item Balanced the demand of planning and teaching multiple subjects while adhering to different project schedules simultaneously.
	\item Led and designed staff development lessons to teach best practices to other teachers within the school and newly hired teachers in the district.
	%\item Worked on a cross-district team of science teachers and administrators to guide the district’s chemistry curriculum adoption process.
	%\item Performed classroom duties, including communication with parents and classroom management, for high school biology, physics, and chemistry.
	%\item Worked collaboratively with other teachers to plan lessons and design curriculum materials.
\end{itemize}
\bigbreak \noindent
%
%\textbf{Special Education Instructional Aide} \hfill \textbf{2009 - 2011}\\
%\textsl{Portland Public Schools, Portland, OR}\\
% Supported middle school and high school students with autism, learning disabilities, developmental delay, and severe social/emotional skill deficits in special education and general education classrooms.\medskip\\
%
%\textbf{Research Assistant} \hfill \textbf{2008}\\
%\textsl{Bradshaw Lab, UO, Eugene, OR}\\
%Performed research concerning the evolution, ecology, and genetic basis of biological clocks in the pitcher plant mosquito.
% -----------------------
%         projects
% -----------------------
\noindent
\makebox[0pt][l]{\rule[-.2\baselineskip]{\linewidth}{.3mm}}\large{\textbf{ADDITIONAL PROJECTS}}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=5pt]
	%\item Built a web application using Node.js and jQuery that allows two users to play the board game Go.
	\item Utilized test-driven development and object oriented design principals into the construction of an Android appointment book application in Java.
	\item Implemented a constraint satisfaction algorithm (AC-3) in Python to solve Star Battle logic puzzles.
	\item Developed a dashboard application in JavaScript for comparing Covid infections between states using the Covid Tracking Project REST API.
	\item Created a Flask web application on Google Cloud’s App Engine using the Vision API to automatically generate accessible HMTL image tags for uploaded photos.
	%\item Collaborated with a team in Agile Sprints and created an AI player program in Java to compete in the 2020 MIT Battlecode tournament.
	%\item Designed and implemented a data model to store Portland freeway data in a Cassandra database cluster on Google Cloud’s Compute Engine virtual machines.
	%\item Created a relational database in PostgreSQL for comparing Dow Jones Industrial Average company data.
	%\item Implemented a bipartite matching algorithm in Python to schedule lessons and activities for elementary school students.
\end{itemize} 
\smallskip
%\textbf{Additional Course Work:} Database Management Systems, Cloud and Cluster Data Management, Functional Programming, Inter-networking Protocols, Artificial Intelligence, Theory of Computation, Software Engineering, Computer Systems Programming, and Operating Systems.\bigskip\\
%Full-Stack Web Development, Advanced Programming in Java, Internet, web, and Cloud Systems, Site Reliability Engineering
%\medskip
\end{document}